---
title: "Case Assignment 8 Xbox Live"
author: "Abhishek Kulkarni, Andrew Scott, and Isha Doshi"
date: "2024-03-03"
output:
  word_document: default
  html_document: default
---

```{r setup, include=FALSE}
knitr::opts_chunk$set(echo = TRUE)
```
#Importing depdencies, reading, and partitioning the data into train, test, and representative dataset
```{r}
library(tidyr)
library(ggplot2)
library(dplyr)
library(sandwich)
library(lmtest)
library(pROC)
library(skimr)
library(purrr)
df=read.csv("xbox_live.csv")
orig_prob=0.0872
reweighted_prob=0.5
df$sweight=ifelse(df$churn == 1,orig_prob / reweighted_prob,(1 - orig_prob) / (1 - reweighted_prob))
train=df[df$training==1,]
test=df[df$training==0,]
rep=df[df$representative==1,]
rep_summary=rep %>%
  select(rural,africa,asia,europe,namerica,oceania,consldays,creditaa,ctrlrs,retired,custcare,gchange,mchange,refurb,months,mdrops,mmins,numgames,over18)%>%
  summarise_all(list(temp_mean = mean, temp_sd = sd, temp_min = min, temp_max = max)) %>%
  gather(stat, val) %>%
  separate(stat, into = c("var", "stat"), sep = "_temp_") %>%
  spread(stat, val) %>%
  select(var, mean, sd, min, max)
```

#Training the logit model and evaluating performance
```{r}
#Logit1
logit1=glm(churn~rural+africa+asia+europe+namerica+oceania+consldays+creditaa+ctrlrs+retired+custcare+gchange+mchange+refurb+months+mdrops+mmins+numgames+over18, 	
                   family = binomial(link='logit'), 
                   weight = sweight,
                   data = train)
train$logit1=predict.glm(logit1, train, type="response")
test$logit1=predict.glm(logit1, test, type="response")
rep$logit1=predict.glm(logit1, rep, type="response")

#AUC (Overfitting test)
print(paste("Train Logit1 AUC",auc(roc(train$churn, train$logit1))))
print(paste("Test Logit1 AUC",auc(roc(test$churn, test$logit1))))

#Summary
coeftest(logit1, vcov = vcovHC(logit1, type="HC1"))

#Comparing actual and predicted churn rates by churn probablity quantiles in the testrepresentative set
rep$logit1_30 <- 31 - ntile(rep$logit1, 30)
ggplot(rep) + 
  stat_summary(aes(x = logit1_30, y = logit1, color="predicted"), fun = "mean", geom = "line") +
  stat_summary(aes(x = logit1_30, y = churn, color="actual"), fun = "mean", geom = "line") +
  xlab("Churn probability quantile") + 
  ylab("Churn Probability") + 
  theme(legend.position = c(0.8, 0.8)) + scale_colour_manual(values=c(predicted="red", actual="blue"))

```
#Identifying major drivers of churn; arranging features by importance and influence in determining churn. Adjusting odds by accounting for disparate scales of measurement for different features
```{r}
logit1_variablenames=variable.names(logit1)
logit1_pvalues=coeftest(logit1, vcov = vcovHC(logit1, type="HC1"))[,4]
logit1_oddsratios=exp(logit1$coef)
variable_summary1=tibble(variable=logit1_variablenames,odds_ratio=logit1_oddsratios,p_value=logit1_pvalues)
variable_summary2=slice(variable_summary1, 2:nrow(variable_summary1))
variable_summary2=variable_summary2 %>% arrange(variable)
variable_summary2$std_dev=rep_summary$sd
variable_summary2$dummy=
  ifelse(variable_summary2$variable == "age_60plus", 1,
         ifelse(variable_summary2$variable == "cooking_addon", 1,
                ifelse(variable_summary2$variable == "crossword_addon", 1,                
                       ifelse(variable_summary2$variable == "educator", 1,  
                              ifelse(variable_summary2$variable == "nyc_metro", 1,  
                                     ifelse(variable_summary2$variable == "print_subscriber", 1,
                                            0 ))))))
variable_summary2$OR_2_SD=
  ifelse(variable_summary2$dummy == 0 & variable_summary2$p_value < 0.05,
         variable_summary2$odds_ratio ^ (2 * variable_summary2$std_dev),
         NA)
variable_summary2$X_orig=ifelse(variable_summary2$dummy == 1,
                                   variable_summary2$odds_ratio,
                                   variable_summary2$OR_2_SD)

variable_summary2$X=ifelse(variable_summary2$p_value < 0.05,
                              variable_summary2$X_orig,
                              NA)

variable_summary2$importance=ifelse(variable_summary2$X > 1,
                                       variable_summary2$X,
                                       1 / variable_summary2$X)
variable_summary3=variable_summary2 %>%
  select(variable, odds_ratio, p_value, std_dev, dummy, OR_2_SD, importance) %>%
  arrange(variable)
variable_summary4=variable_summary3 %>%
  filter(p_value < 0.05) %>%
  arrange(desc(importance))
variable_summary5=variable_summary4 %>%
  mutate(effect = ifelse(odds_ratio > 1, "+", "-")) %>%
  select(variable, importance, effect)

print(variable_summary5)
```

#Simulating the effect of offering 6 months of extended subscripton (lead to decrease of ~1% in churn)
```{r}
df$churn_prob <- predict.glm(logit1, df, type="response")
df$months_orig <- df$months
df$months <- df$months_orig + 6
df$churn_prob2 <- predict.glm(logit1, df, type="response")
df %>% filter(representative == 1) %>% select(churn_prob, churn_prob2) %>% summary()
```